---
output: html_document
---
For SVM and TUNE

```{r}
library('e1071')
setwd('D:\\packages\\sem5\\AI')
```




Reading the data
```{r}

orgdata<-read.csv("wdbc.csv",header=T)
n=nrow(orgdata)
c=ncol(orgdata)
n
c
(class(orgdata))
```
Normalisation and separation
```{r}
orgdata[, -c(1,2)] <- scale(orgdata[, -c(1,2)])

BenignData=orgdata[which(orgdata$diagnosis=='B'),-c(1,2)]
MalignantData=orgdata[which(orgdata$diagnosis=='M'),-c(1,2)]
data=orgdata[,-c(1,2)]
```
To calculate Optimum K centroids for B,<br/>
We calculate davg which is the average distance of each node from its cluster representative.
Then we calculate dmin for each k which is the min distance between any pair of centroids<br/>
We intend to calculate the validity ratio as davg/dmin, this means that we want to reduce the distance between the nodes and their centroids and maximise the distance between centroids.Then we find the optimum k as the number that corresponds to the minimum validity ratio<br/>
<br/>
<br/>
We do for Benign data first,</br>
We set seed to generate the same random number for the same value

```{r}

BenignValRatio=c()

set.seed(100);
for(k in 2:30)
{
  
    davg=0
    #KMEANS returns centroids centres ($centers) and the which cluster a node belongs to($cluster) 
    BenignCluster <- kmeans(BenignData, k, nstart = 20)
    
    #Finding dAvg
    for(i in 1:nrow(BenignData))
    {
      davg=davg+dist(rbind(BenignData[i,],BenignCluster$centers[BenignCluster$cluster[i],]))   
    }
    davg=davg/nrow(BenignData)
    dmin=Inf
    for(i in 1:(k-1))
    {
      y=BenignCluster$centers[i,]
      x=BenignCluster$centers[(i+1):k,]
      if(i==(k-1))
      {
        dis=dist(rbind(x,y))
      }
      else
      {
        dis=min(apply(x,1,function(x,y)dist(rbind(x,y)),y))     #Getting the minimum distance
      }
      if(dmin>dis)
      {
        dmin=dis
      }
    }
    ValRatio=davg/dmin
    BenignValRatio=c(BenignValRatio,ValRatio)    
}
BenignValRatio

```
Now we do for malignant
```{r}
MalignantValRatio=c()
for(k in 2:30)
{
  
    #KMEANS returns centroids centres ($centers) and the which cluster a node belongs to($cluster) 
    MalignantCluster <- kmeans(MalignantData, k, nstart = 20)
    davg=0
    #Finding dAvg
    for(i in 1:nrow(MalignantData))
    {
      
      davg=davg+dist(rbind(MalignantData[i,],MalignantCluster$centers[MalignantCluster$cluster[i],]))   
    
    }
    davg=davg/nrow(MalignantData)
    dmin=Inf
    for(i in 1:(k-1))
    {
      y=MalignantCluster$centers[i,]
      x=MalignantCluster$centers[(i+1):k,]
      
      if(i==(k-1))
      {
        dis=dist(rbind(x,y))
      }
      else
      {
        dis=min(apply(x,1,function(x,y)dist(rbind(x,y)),y))     #Getting the minimum distance
      }
      if(dmin>dis)
      {
        dmin=dis
      }
    }
    ValRatio=davg/dmin
    MalignantValRatio=c(MalignantValRatio,ValRatio)    
}
MalignantValRatio


```
Now We plot the k vs validity ratio graphs

```{r}
krange=(2:30)
plot(krange, BenignValRatio, xlim=range((2:30)), ylim=range(BenignValRatio), xlab="k", ylab="ValRatio",     main = "Benign")
lines(krange[order(krange)], BenignValRatio[order(krange)], xlim=range(krange), ylim=range(BenignValRatio),col="blue")

plot(krange, MalignantValRatio, xlim=range((2:30)), ylim=range(MalignantValRatio), xlab="k", ylab="ValRatio",     main ="Malignant")
lines(krange[order(krange)], MalignantValRatio[order(krange)], xlim=range(krange), ylim=range(MalignantValRatio),col="red")
```

Taking K=3 we proceed as per the research paper

```{r}
BenignCluster <- kmeans(BenignData, 3, nstart = 20)
MalignantCluster <- kmeans(MalignantData, 3, nstart = 20)

```

Now we define new features for all the nodes. We define new 6 features that reduces the feature space to 6 from 32. The similarity between the untested and the symbolic tumors plays an important role. To measure the similarity we use a membership function as per the research paper.

Finding Min and Max for each type and each cluster of each feature
Example:
Among all 1st feature that belongs to first cluster find minimum 
Do similarly for all others too!


```{r}
#Finding MIN and MAX of each type
minBenign=aggregate(BenignData, by=list(BenignCluster$cluster), FUN=min)

maxBenign=aggregate(BenignData, by=list(BenignCluster$cluster), FUN=max)

minMalignant=aggregate(MalignantData, by=list(MalignantCluster$cluster), FUN=min)

maxMalignant=aggregate(MalignantData, by=list(MalignantCluster$cluster), FUN=max)

minBenign=minBenign[2:31]
maxBenign=maxBenign[2:31]
minMalignant=minMalignant[2:31]
maxMalignant=maxMalignant[2:31]

#For removing the cluster numbers as a column
#Example of one
minBenign
```


```{r}

Benigncenters=BenignCluster$centers
Malignantcenters=MalignantCluster$centers
BenignDen=c()
MalignantDen=c()
for(i in 1:3)
{
  #For each we find the max value of centroid value minus min value or max value of the same feature
  #Either of these must give the maximum
  temp1=apply(rbind(abs(Benigncenters[i,]-minBenign[i,]),abs(maxBenign[i,]-Benigncenters[i,])),2,max)
  
  BenignDen=rbind(BenignDen,temp1)
  
  temp2=apply(rbind(abs(Malignantcenters[i,]-minMalignant[i,]),abs(maxMalignant[i,]-Malignantcenters[i,])),2,max)
  
  
   MalignantDen=rbind(MalignantDen,temp2)
}
#Can also use when 3 rows are aready present,Initially throws error
#MalignantDen[1:3,]=apply(rbind(abs(Malignantcenters[1:3,]-minMalignant[1:3,]),abs(maxMalignant[1:3,]-M#alignantcenters[1:3,])),2,max)

```
We create new features for each row and this is the training data!!
```{r}
F=ncol(data)
for(i in 1:n)
{
  newfeature=c()
  for(c in 1:3)
  {
    val=0
    for(f in 1:F)
    {
      if(data[i,f]>=minBenign[c,f] & data[i,f]<=maxBenign[c,f])
      {
        val=val+1-(abs(Benigncenters[c,f]-data[i,f])/BenignDen[c,f])
      }
    }
    val=val/F
    newfeature=c(newfeature,val)
  }
  for(c in 1:3)
  {
    val=0
    for(f in 1:F)
    {
      if(data[i,f]>=minMalignant[c,f] & data[i,f]<=maxMalignant[c,f])
      {
        val=val+1-(abs(Malignantcenters[c,f]-data[i,f])/MalignantDen[c,f])
      }
    }
    val=val/F
    newfeature=c(newfeature,val)
  }
  
  if(i==1)
  {
    finaldata=newfeature
  }
  else
  {
    finaldata=rbind(finaldata,newfeature)
  }
}

finaldata
```


```{r}
class=orgdata[,2]
svm_tune <- tune(svm, train.x=finaldata, train.y=class, kernel="radial", ranges=list(cost=10^(-1:2), gamma=c(.1,.5,1)))
#plot(svm_tune)
print(svm_tune)
model <- svm(finaldata, class,kernel = 'radial', gamma = 0.1, cost = 10, cross=10)
summary(model)

```

